The 4th Workshop on Sustainable Software: Best Practices and Experiences (WSSSPE4)

### 2016-06-10 WSSSPE4_proposal/WSSSPE4_proposal.tex
fixing margins and list spacing

 \geometry{
 letterpaper,
 total={215.9mm,279.4mm},
 left=20mm,
 right=20mm,
 top=20mm,
 bottom=20mm,
 bindingoffset=0mm
 }

@@

\title{The 4th Workshop on Sustainable Software: Best Practices and Experiences (WSSSPE4)
}
\author{Gabrielle Allen, University of Illinois Urbana--Champaign \\
	Daniel S.\ Katz, University of Illinois Urbana--Champaign \\
	Kyle E.\ Niemeyer, Oregon State University
	}
\date{}                                           % Activate to display a given date or no date

@@

Topics of interest include but are not limited to:
\begin{itemize}
\item Development and Community
\begin{itemize}
\item Best practices for developing sustainable software
\item Models for funding specialist expertise in software collaborations
\item Software tools that aid sustainability
\item Academia/industry interaction
\item Refactoring/improving legacy scientific software
\item Engineering design for sustainable software
\item Metrics for the success of scientific software
\item Adaptation of mainstream software practices for scientific software
\end{itemize}
\item Professionalization
\begin{itemize}
\item Career paths
\item RSE as a brand
\item RSE outside of the UK or Europe
\item Increase incentives in publishing, funding and promotion for better software
\end{itemize}
\item Training
\begin{itemize}
\item Training for developing sustainable software
\item Curriculum for software sustainability
\end{itemize}
\item Credit
\begin{itemize}
\item Making the existing credit and citation ecosystem work better for software
\item Future credit and citation ecosystem
\item Software contributions as a part of tenure review
\item Case studies of receiving credit for software contributions
\item Awards and recognition that encourage sustainable software
\end{itemize}
\item Software publishing
\begin{itemize}
\item Journals and alternative venues for publishing software
\item Review processes for published software
\end{itemize}
\item Software discoverability/reuse
\begin{itemize}
\item Proposals and case studies
\end{itemize}
\item Reproducibility and testing
\begin{itemize}
\item Reproducibility in conferences and journals
\item Best practices for code testing and code review
\end{itemize}
\end{itemize}

@@

\begin{quote}
Example idea paper topics include:
\begin{itemize}
\item Adaptation of industrial software engineering principles into the research software community with a plan to fund the work
\item Funding and scaling software carpentry style training in advanced topics
Infrastructure and funding for community maintenance of open use research software
\item Scaling the SSI beyond the UK
\item Specific proposals of how to bridging/network the various research software engineering communities in scalable manner without destroying independence and unique foci of each community
\end{itemize}
\end{quote}

@@

The WSSSPE4 organizing committee comprises 
\begin{itemize}
\item Gabrielle Allen, University of Illinois Urbana-Champaign, USA
\item Jeffrey Carver, University of Alabama, USA
\item Sou-Cheng T. Choi, Illinois Institute of Technology, USA
\item Tom Crick, Cardiff Metropolitan University, UK
\item Michael R. Crusoe, Common Workflow Language project
\item Sandra Gesing, University of Notre Dame, USA
\item Robert Haines, University of Manchester, UK
\item Michael Heroux, Sandia National Laboratories, USA
\item Lorraine J. Hwang, University of California, Davis, USA
\item Daniel S. Katz, University of Illinois Urbana-Champaign, USA
\item Kyle E. Niemeyer, Oregon State University, USA
\item Manish Parashar, Rutgers University, USA
\item Colin C. Venters, University of Huddersfield, UK
\end{itemize}

@@

\begin{itemize}
\item Introduction
\item Keynote
\item Lightning talks
\item Updates on actions and activities from WSSSPE3 working groups
\item Discussion and planning for the remainder of WSSSPE4
\end{itemize}

@@

\begin{itemize}
\item Track 1: This will be a set of working sessions with a facilitated discussion, breakout sessions, report backs, and active writing towards the track goal of defining a vision of the future of open-use research software, and a plan of activities that are needed to get there.
\item Track 2: Presentations of position papers, experience papers, previously published works, and demos; and breakout sessions or unconference sessions.
\end{itemize}

@@

\begin{itemize}
\item Panel on best practices
\item Summary and discussion of each tracks’ progress
\item Planning for future events
\end{itemize}

>>>>

 \geometry{
 letterpaper,
 total={215.9mm,279.4mm},
 left=25.4mm,
 right=25.4mm,
 top=25.4mm,
 bottom=25.4mm,
 bindingoffset=0mm
 }

 \newenvironment{shortlist}{
        \vspace*{-0.8em}
  \begin{itemize}
  \setlength{\itemsep}{-0.3em}
}{
  \end{itemize}
        \vspace*{-0.6em}
}

 \newenvironment{shortlist2}{
        \vspace*{-0.5em}
  \begin{itemize}
  \setlength{\itemsep}{-0.1em}
}{
  \end{itemize}
        \vspace*{-0.3em}
}
 \newenvironment{shortenum}{
        \vspace*{-0.8em}
  \begin{enumerate}
  \setlength{\itemsep}{-0.3em}
}{
  \end{enumerate}
        \vspace*{-0.6em}
}

@@

\title{The 4th Workshop on Sustainable Software: Best Practices and Experiences (WSSSPE4)
}
\author{Daniel S.\ Katz, University of Illinois Urbana--Champaign \\
        Gabrielle Allen, University of Illinois Urbana--Champaign \\
	Kyle E.\ Niemeyer, Oregon State University
	}
\date{}                                           % Activate to display a given date or no date

@@

Topics of interest include but are not limited to:
\begin{shortlist}
\item Development and Community
\begin{shortlist}
\item Best practices for developing sustainable software
\item Models for funding specialist expertise in software collaborations
\item Software tools that aid sustainability
\item Academia/industry interaction
\item Refactoring/improving legacy scientific software
\item Engineering design for sustainable software
\item Metrics for the success of scientific software
\item Adaptation of mainstream software practices for scientific software
\end{shortlist}
\item Professionalization
\begin{shortlist}
\item Career paths
\item RSE as a brand
\item RSE outside of the UK or Europe
\item Increase incentives in publishing, funding and promotion for better software
\end{shortlist}
\item Training
\begin{shortlist}
\item Training for developing sustainable software
\item Curriculum for software sustainability
\end{shortlist}
\item Credit
\begin{shortlist}
\item Making the existing credit and citation ecosystem work better for software
\item Future credit and citation ecosystem
\item Software contributions as a part of tenure review
\item Case studies of receiving credit for software contributions
\item Awards and recognition that encourage sustainable software
\end{shortlist}
\item Software publishing
\begin{shortlist}
\item Journals and alternative venues for publishing software
\item Review processes for published software
\end{shortlist}
\item Software discoverability/reuse
\begin{shortlist}
\item Proposals and case studies
\end{shortlist}
\item Reproducibility and testing
\begin{shortlist}
\item Reproducibility in conferences and journals
\item Best practices for code testing and code review
\end{shortlist}
\end{shortlist}

@@

\begin{quote}
Example idea paper topics include:
\begin{shortlist}
\item Adaptation of industrial software engineering principles into the research software community with a plan to fund the work
\item Funding and scaling software carpentry style training in advanced topics
Infrastructure and funding for community maintenance of open use research software
\item Scaling the SSI beyond the UK
\item Specific proposals of how to bridging/network the various research software engineering communities in scalable manner without destroying independence and unique foci of each community
\end{shortlist}
\end{quote}

@@

The WSSSPE4 organizing committee comprises 
\begin{shortlist}
\item Gabrielle Allen, University of Illinois Urbana-Champaign, USA
\item Jeffrey Carver, University of Alabama, USA
\item Sou-Cheng T. Choi, Illinois Institute of Technology, USA
\item Tom Crick, Cardiff Metropolitan University, UK
\item Michael R. Crusoe, Common Workflow Language project
\item Sandra Gesing, University of Notre Dame, USA
\item Robert Haines, University of Manchester, UK
\item Michael Heroux, Sandia National Laboratories, USA
\item Lorraine J. Hwang, University of California, Davis, USA
\item Daniel S. Katz, University of Illinois Urbana-Champaign, USA
\item Kyle E. Niemeyer, Oregon State University, USA
\item Manish Parashar, Rutgers University, USA
\item Colin C. Venters, University of Huddersfield, UK
\end{shortlist}

@@

\begin{shortlist}
\item Introduction
\item Keynote
\item Lightning talks
\item Updates on actions and activities from WSSSPE3 working groups
\item Discussion and planning for the remainder of WSSSPE4
\end{shortlist}

@@

\begin{shortlist}
\item Track 1: This will be a set of working sessions with a facilitated discussion, breakout sessions, report backs, and active writing towards the track goal of defining a vision of the future of open-use research software, and a plan of activities that are needed to get there.
\item Track 2: Presentations of position papers, experience papers, previously published works, and demos; and breakout sessions or unconference sessions.
\end{shortlist}

@@

\begin{shortlist}
\item Panel on best practices
\item Summary and discussion of each tracks’ progress
\item Planning for future events
\end{shortlist}
